\item ``Robust Likelihoods for Inflationary Gravitational Waves from Maps of Cosmic Microwave Background Polarization'', E.\, R.\, Switzer, D.\, J.\, Watts, {\it ArXiv e-prints} (2016).
\item ``Interpreting the Unresolved Intensity of Cosmologically Redshifted Line Radiation'', E.\, R.\, Switzer, T.\,-C.\, Chang, K.\, W.\, Masui, U.\,-L.\, Pen, and T.\, C.\, Voytek, {\it ApJ}, 815, 51 (2015).
\item ``Erasing the Milky Way: new cleaning technique applied to GBT intensity mapping data'', L.\, Wolz, C.\, Blake, F.\, B.\, Abdalla, C.\, M.\, Anderson, T.\,-C.\, Chang, Y.\,-C.\, Li, K.\, W.\, Masui, E.\, Switzer, U.\,-L.\, Pen, T.\, C.\, Voytek, and J.\, Yadav, {\it ArXiv e-prints} (2015).
\item ``Erasing the Variable: Empirical Foreground Discovery for Global 21 cm Spectrum Experiments'', E.\, R.\, Switzer, A.\, Liu, {\it ApJ}, 793, 102 (2014).
\item ``The Atacama Cosmology Telescope: dusty star-forming galaxies and active galactic nuclei in the Southern survey'', D.\, Marsden, M.\, Gralla, T.\, A.\, Marriage, E.\, R.\, Switzer, ACT Collaboration, {\it MNRAS}, 439, 1556 (2014).
\item ``The Atacama Cosmology Telescope: cosmological parameters from three seasons of data'', J.\, L.\, Sievers, R.\, A.\, Hlozek, M.\, R.\, Nolta, ACT Collaboration, {\it JCAP}, 10, 060 (2013).
\item ``Determination of z $\sim$ 0.8 neutral hydrogen fluctuations using the 21 cm intensity mapping autocorrelation'', E.\, R.\, Switzer, K.\, W.\, Masui, GBT Collaboration, {\it MNRAS}, 434, L46 (2013).
\item ``Sunyaev-Zel'dovich signal processing and temperature-velocity moment method for individual clusters'', J.\, Chluba, E.\, Switzer, K.\, Nelson, and D.\, Nagai, {\it MNRAS}, 430, 3054 (2013).
\item ``Constraints on Perturbations to the Recombination History from Measurements of the Cosmic Microwave Background Damping Tail'', M.\, Farhang, J.\, R.\, Bond, J.\, Chluba, and E.\, R.\, Switzer, {\it ApJ}, 764, 137 (2013).
\item ``Measurement of 21 cm Brightness Fluctuations at z $\sim$ 0.8 in Cross-correlation'', K.\, W.\, Masui, E.\, R.\, Switzer, GBT Collaboration, {\it ApJL}, 763, L20 (2013).
\item ``The Atacama Cosmology Telescope: Data Characterization and Mapmaking'', R.\, Dunner, M.\, Hasselfield, T.\, A.\, Marriage, J.\, Sievers, ACT Collaboration, {\it ApJ}, 762, 10 (2013).
\item ``Evidence of Galaxy Cluster Motions with the Kinematic Sunyaev-Zel'dovich Effect'', N.\, Hand, ACT Collaboration, {\it PRL}, 109, 041101 (2012).
\item ``Correlations in the (Sub)millimeter Background from ACT x BLAST'', A.\, Hajian, M.\, P.\, Viero, ACT Collaboration, {\it ApJ}, 744, 40 (2012).
\item ``The Steppenwolf: A Proposal for a Habitable Planet in Interstellar Space'', D.\, S.\, Abbot, E.\, R.\, Switzer, {\it ApJL}, 735, L27 (2011).
\item ``Overview of the Atacama Cosmology Telescope: Receiver, Instrumentation, and Telescope Systems'', D.\, S.\, Swetz, ACT Collaboration, {\it ApJS}, 194, 41 (2011).
\item ``The HeI 584 A forest as a diagnostic of helium reionization'', M.\, McQuinn, E.\, R.\, Switzer, {\it MNRAS}, 408, 1945 (2010).
\item ``Extragalactic Millimeter-wave Sources in South Pole Telescope Survey Data: Source Counts, Catalog, and Statistics for an 87 Square-degree Field'', J.\, D.\, Vieira, T.\, M.\, Crawford, E.\, R.\, Switzer, SPT Collaboration, {\it ApJ}, 719, 763 (2010).
\item ``A Method for Individual Source Brightness Estimation in Single- and Multi-band Data'', T.\, M.\, Crawford, E.\, R.\, Switzer, W.\, L.\, Holzapfel, C.\, L.\, Reichardt, D.\, P.\, Marrone, and J.\, D.\, Vieira, {\it ApJ}, 718, 513 (2010).
\item ``Redshifted intergalactic 3He+ 8.7 GHz hyperfine absorption'', M.\, McQuinn, E.\, R.\, Switzer, {\it PRD}, 80, 063010 (2009).
\item ``Primordial helium recombination III: Thomson scattering, isotope shifts, and cumulative results'', E.\, R.\, Switzer, C.\, M.\, Hirata, {\it PRD}, 77, 083008 (2008).
\item ``Primordial helium recombination II: Two-photon processes'', C.\, M.\, Hirata, E.\, R.\, Switzer, {\it PRD}, 77, 083007 (2008).
\item ``Primordial helium recombination I: Feedback, line transfer, and continuum opacity'', E.\, R.\, Switzer, C.\, M.\, Hirata, {\it PRD}, 77, 083006 (2008).
\item ``Ionizing radiation from hydrogen recombination strongly suppresses the lithium scattering signature in the CMB'', E.\, R.\, Switzer, C.\, M.\, Hirata, {\it PRD}, 72, 083002 (2005).
\item ``Nonlinear cosmological matter power spectrum with massive neutrinos: The halo model'', K.\, Abazajian, E.\, R.\, Switzer, S.\, Dodelson, K.\, Heitmann, and S.\, Habib, {\it PRD}, 71, 043507 (2005).
